Draft

### 2020-09-24 Final.Rmd
fixed problems in Ruben's comments.

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}\doublespacing
  - \usepackage[hyphens]{url}
fontsize: 12pt
geometry: margin=1in
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
link-citations: yes
bibliography: references.bib
---

@@

This paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on optimal probabilistic forecasting method which is recently proposed to conduct a forecast using scoring rules instead of the conventional likelihood function in the frequentist econometrics. In particular, the role of optimal forecasts in predicting S&P 500 returns, the Value-at-Risk and the VIX Volatility Index. We find that the performance of optimal probabilistic forecasts is insensitive to the form of misspecification but improves as the degree of misspecification increases. After the Global financial crisis, predictions that are optimal according to the focused scoring rule that rewards predictive accuracy in a tail are substantially more accurate at predicting observations in said tail than the alternatives, including likelihood-based predictions.

@@

This paper explores the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal probabilistic forecasts in financial applications.

Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable than point and interval forecasts to forecasters. However, previous approaches to prediction - including probabilistic methods - typically assume that the predictive model correctly specifies the process that has generated the observations. In practice, the assumed model underpinning the likelihood function will almost certainly differ from the unknown true data generating process (DGP). This model misspecification problem has been an ongoing issue for conventional likelihood-based prediction.

As an alternative to likelihood-based prediction, scoring rules have been proposed as a means of producing probabilistic forecasts. A variety of alternative proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand (Gneiting & Raftery, 2007). Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al. (2020). Among all these investigations, it is the censored likelihood score (CLS) proposed originally by Diks, Panchenko & van Dijk (2011), that captures our attention, since its ‘focusing’ feature has great potential in financial risk management. In other words, CLS allows a forecaster to focus on predicting any particular region of interest more accurately and, therefore, is expected to make an important contribution to risk prediction in financial settings.

The ‘optimal’ probabilistic forecast has been discussed in Loaiza-Maya et al. (2020). It refers to a predictive probability distribution that is optimal according to a user-specified scoring rule. Whilst some empirical investigations were undertaken, these were primarily illustrative, with there being much scope left for exploring the performance of optimal methods in forecasting different types of financial measures, and under different assumed models.

This research paper extends the work of Loaiza-Maya et al. (2020) by investigating the effect of the form and degree of model misspecification on optimal forecast performance in particular financial settings; in particular by conducting an empirical analysis of how optimal forecasts perform in Value-at-Risk (VaR), Volatility Index (VIX) and portfolio optimization applications. Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.

@@

Optimal probabilistic forecasts discussed in this paper refer to the forecasts produced from a model that is ‘optimized’ based on a user-specified proper scoring rule will perform the best out-of-sample – according to that same score (Loaiza-Maya et al.,2020).

Scoring rules are a type of criterion function that can be optimized to produce an optimal estimator and thus, a probabilistic prediction derived from this optimal estimator and an assumed model. They also play the role of encouraging forecasters to make careful and honest assessments in elicitation of subjectivist Bayesians, and evaluating and ranking competitive probabilistic forecasts, based on the predictive distribution and materialized events or values, by assigning a numerical score [@waite2005; @gneiting2007]. Therefore, the crucial importance of the propriety of scoring rules must be emphasized for their usage because improper scoring rules will assign a higher average score to an incorrect density forecast (Gneiting & Raftery, 2007). Consequently, forecasts based on improper scoring rules will not be ‘optimal’.

Suppose P and Q are predictive distributions and Q is the best forecast given all the available information. S(P,Q) denotes the expected value of S(P,$\cdot$) under Q. A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q (Gneiting & Raftery, 2007).

In terms of producing probabilistic forecasts, scoring rules can replace the conventional likelihood function in frequentist and Bayesian predictions; see Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al. (2020). Supposing the scoring rule is positively oriented, an estimator $\hat \theta_n$ obtained by maximizing a scoring rule $S_n(\theta)$ is said to be 'optimal' based on this scoring rule. 
\begin{equation} \label{eq:1}
\hat \theta_n=arg \max_\theta S_n(\theta)
\end{equation}
Under certain conditions, including that the scoring rule is 'proper', $\hat \theta_n \to \theta_0 \ as \ T \to \infty$,
where $\theta_0$ is the true parameter and T is the total sample size of a time series variable $y_t$. The predictions conditional on this optimal estimator, $p(y_{T+1}|M,\hat \theta_n,y_{1:T})$, is said to be produced from a model that is 'optimized' according to a proper scoring rule. ^[M refers to the assumed model and it is omitted in the following notation for simplicity, since the assumed model does not change.]

In addition, in terms of evaluating predictions, it is usually the average score ($\bar S_n$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules (Gneiting & Reftery, 2007). 
\begin{equation} \label{eq:sbar}
\bar S_n = \frac{1}{T}\sum_{t=1}^TS_n(p_{t+1},y_t)
\end{equation}
For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates, on the condition the scoring rule being proper.

## 2.2 Some commonly used scoring rules 
A variety of scoring rules have been developed to tackle different problems. Some commonly used proper scoring rules are adopted in the analyses in this paper, such as the logarithmic score (LS), the continuously ranked probability score (CRPS) and the censored likelihood score (CLS).

The logarithmic score is defined as in $\eqref{eq:ls}$ where $p_t$ is the predictive density. 
\begin{equation} \label{eq:ls}
S_{LS}(p_{t-1}, y_t) = log[p_{t-1}(y_t)]
\end{equation}
It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters (Bickel, 2007). One common usage of the logarithmic score in frequentist econometrics is the maximum likelihood estimation (MLE).
\begin{equation} \label{eq:mle}
\hat \theta_{MLE}=arg \max_\theta \{log[p(\boldsymbol y|\theta)]\}
\end{equation}
It is included as a benchmark in the following numerical and empirical investigations of the performance of optimal forecasts due to its asymptotically optimal and efficient characteristics under the correctly specified log-likelihood function.

However, the logarithmic score is criticized for its unboundedness and its local property. Bernardo (1979) states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state". Gneiting & Raftery (2007) also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event. Gneiting & Raftery (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in $\eqref{eq:crps}$ 
\begin{equation} \label{eq:crps}
CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P(y)-I(y\geq x_t)]^2dy
\end{equation}
where P is the cumulative distribution function, *I* is the indicator function, and x is the materialized event.

The formula can be simplified to $\eqref{eq:crnorm}$ if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
\begin{equation} \label{eq:crnorm}
CRPS(N_{t-1},x_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x_t-\mu}{\sigma})-\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
\end{equation}
where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the Gaussian predictive distribution.

Both LS and CRPS are used for producing and evaluating the entire predictive densities. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011). Diks, Panchenko & van Dijk, (2011) propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast. Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy. It is defined as in $\eqref{eq:cls}$
\begin{equation} \label{eq:cls}
S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
\end{equation}
where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$. Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.

@@

The degree of model misspecification impacts the performance of optimal forecasts. The greater the degree of misspecification is, the more benefits are gained from optimal forecasts in both Bayesian and frequentist predictions, conditional on the assumed predictive model being compatible; see [@fbp2019], [@optimal]. The simulation analysis in this paper will extend the exploration in this field and ask the question ‘Will the performance of optimal forecasts change when a different form of misspecification occurs?’.

In order to set the scene for the financial application analyses in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and volatility. Specific simulation scenarios are listed in the following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).

\begin{table}[!h]
\centering
\begin{tabular}{|c|c|c|}
\hline
\multicolumn{3}{|c|}{\textbf{Simulation design}} \\ \hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & Stochastic volatility inversion copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline

\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
\end{tabular}
\end{table}

@@

Copulas “reweight” the marginal densities to produce a joint density that captures the dependence among random variables, which can be applied to conditional distributions for forecasting purposes as shown in $\eqref{eq:copula}$. 
\begin{equation} \label{eq:copula}
H_t(x,y|\mathcal{F}_{t-1})=C_t(F_t(x|\mathcal{F}_{t-1}),G_t(y|\mathcal{F}_{t-1})|\mathcal{F}_{t-1})
\end{equation}
where $X_t$ and $Y_t$ are random variables with conditional marginal densities denoted by $F_t$ and $G_t$, $\mathcal{F}_t$ is an information set available at time t, and $H_t$ denotes the conditional joint distribution of $X_t$ and $Y_t$ [@fan2014].

The stochastic volatility inversion copula model used in this section allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns but is not allowed if we use state space models alone [@inversion2018].

In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP in Scenario (i) and (ii).

Optimal forecasts can outperform predictions produced by conventional methods out of sample; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.(2020); but the underlying reasons driving this phenomenon are still under investigation. Loaiza-Maya, Martin & Frazier (2019) propose a new method, focused Bayesian prediction (FBP), which replaces the conventional likelihood function with the censored likelihood score. In their simulated and empirical analysis, Focused Bayes outperforms exact Bayes which uses the logarithmic score for updating the prior probability and they also point out that model misspecification plays a role in the performance of Focused Bayes since focusing incorrectly can harm.

Loaiza-Maya et al.(2020) extend the above discussion to frequentist probability forecasting. They address questions about when we can/cannot benefit from optimal probabilistic forecasts out of sample. Loaiza-Maya et al.(2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance. Coherence means that the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score. Strict coherence happens when the optimal prediction is strictly preferable given that score. Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules: $S_1$ and $S_2$. The predictive density $S_n(P^{t-1}_{\boldsymbol{\hat \theta_n}},y_t)$ is said to be coherent if 
\begin{equation} \label{eq:coh1}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
\end{equation}
\begin{equation} \label{eq:coh2}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
\end{equation}
It is said to be strictly coherent if $\eqref{eq:coh1}$ and $\eqref{eq:coh2}$ are strict inequalities.

Building on the previous research in this field, we conduct a numerical analysis in this section to further investigate the effects of the form and degree of model misspecification on the performance of optimal forecasts.

MLE is a frequently used estimation method in frequentist prediction. It often works with the log-likelihood, which corresponds to the logarithmic scoring rule. Therefore, we use the predictions produced by MLE (LS) as the benchmark of the following comparisons. Besdies, the tails of a density are important for risk management in finance so that we decide to apply the focused scoring rule to the 10%, 20%, 80% and 90% tails of the distribution, corresponding to the risks of long and short portfolios. Certain aspects of the methodology used in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) are adopted here. We conduct each simulation scenario as follows:

Let $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ be the one-step-ahead prediction based on the assumed model, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$ ($P(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$) be the predictive probabilistic (cumulative probabilistic) distribution at time t.

@@

  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}$

\begin{equation} \label{eq:theta}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{equation}
\begin{equation} \label{eq:score}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
\end{equation}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:CLS}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]

\begin{equation} \label{eq:LS}
S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
\end{equation}
\begin{equation} \label{eq:CRPS}
S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
\end{equation}
\begin{equation} \label{eq:CLS}
S_{CLS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
\end{equation}
4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
\begin{equation} \label{eq:avgscore}
\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
\end{equation}

>>>>

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}\doublespacing
  - \usepackage[hyphens]{url}
  - \usepackage{boondox-cal}
fontsize: 12pt
geometry: margin=1in
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
link-citations: yes
bibliography: references.bib
---

@@

With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification. Building off previous research, this paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score. In particular, we assess the predictive performance of optimal forecasts in two empirical contexts: prediction of the Value-at-Risk and prediction of the VIX Volatility Index. Results show that the greater the degree of model misspecification, the more beneficial is optimal prediction, no matter which form of model misspecification is. Predictions that are optimal according to the censored likelihood score that rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.

@@

This paper explores the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal forecasts in financial applications.

Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable than point and interval forecasts to forecasters. However, previous approaches to prediction - including probabilistic methods – typically assume that the predictive model or the likelihood function correctly specifies the true data generating process (DGP) or the true DGP lies in the model pools, which is almost certainly untrue in practice. Optimal probabilistic forecasting refers to the construction of a predictive probability distribution that is optimal according to a user-specified proper scoring rule [@optimal]. It is not constructed based on the conventional likelihood function but on a proper scoring rule that matches the specific problem at hand. Optimal probabilistic forecasts aim to improve the predictive accuracy of a misspecified model, whilst the conventional approaches to probabilistic forecasting focus on the development of increasingly less misspecified models that can potentially yield better probabilistic forecasts.

A variety of proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand [@gneiting2007]. Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see @opschoor2017, @fbp2019 and @optimal. Among all these investigations, it is the censored likelihood score (CLS) proposed originally by @diks2011, that captures our attention for the purpose of demonstrating the application of optimal probabilistic forecasts in finance. Its ‘focusing’ feature has great potential in financial risk management. In other words, CLS allows a forecaster to focus on predicting any particular region of interest more accurately. Therefore, its usage in this context represents an important contribution to risk prediction in financial settings.

Whilst some empirical investigations about the performance of optimal forecasts were undertaken in @optimal, these were primarily illustrative, and left much scope for exploring the performance of optimal probabilistic forecasting methods in forecasting different types of financial measures, and under different assumed models.

This research paper extends the work of @optimal by investigating the effect of the form and degree of model misspecification on the performance of optimal probabilistic forecasts in financial settings; in particular by conducting empirical analyses of how optimal forecasts perform in predicting the Value-at-Risk (VaR) and the VIX Volatility Index (VIX). Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.

@@

Scoring rules are a type of criterion function that can be optimized to produce an optimal estimator and thus, a probabilistic prediction derived from this optimal estimator and an assumed model. They also play the role of encouraging forecasters to make careful and honest assessments in elicitation of subjectivist Bayesians, and evaluating and ranking competitive probabilistic forecasts, based on the predictive distribution and materialized events or values, by assigning a numerical score [@waite2005; @gneiting2007]. Therefore, the crucial importance of the propriety of scoring rules must be emphasized for their usage because improper scoring rules will assign a higher average score to an incorrect density forecast [@gneiting2007]. Consequently, forecasts based on improper scoring rules will not be ‘optimal’.

Suppose P and Q are predictive distributions and Q is the best forecast given all the available information. S(P,Q) denotes the expected value of S(P,$\cdot$) under Q. A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q [@gneiting2007].

In terms of producing probabilistic forecasts, scoring rules can replace the conventional likelihood function in frequentist and Bayesian predictions; see @fbp2019 and @optimal. Supposing the scoring rule is positively oriented, then an estimator $\hat \theta$ obtained by maximizing a scoring rule $S(\theta)$ is said to be 'optimal' based on this scoring rule. 
\begin{equation} \label{eq:1}
\hat \theta =arg \max_\theta S(\theta)
\end{equation}
Under certain conditions, including that the scoring rule is 'proper', $\hat \theta \to \theta_0 \ as \ \mathcal{T} \to \infty$,
where $\theta_0$ is the true parameter value and $\mathcal{T}$ is the total sample size of a time series variable $y_t$. The predictive distribution based on this optimal estimator, $p(y_{T+1}|M,\hat \theta,y_{1:T})$, has been produced from the assumed model by optimizing a proper scoring rule. ^[M refers to the assumed model and it is omitted in the following notation for simplicity, since the assumed model does not change.]

In addition, in terms of evaluating predictions, scoring rules assign numerical values to density forecasts, addressing both sharpness and calibration simultaneously. It is usually the average score ($\bar S$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules [@gneiting2007]. 
\begin{equation} \label{eq:sbar}
\bar S = \frac{1}{T}\sum_{t=1}^T S(p_{t+1},y_t)
\end{equation}
For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates, on the condition of the scoring rule being proper.

## 2.2 Some commonly used scoring rules

A variety of scoring rules have been developed to tackle different problems. Some commonly used proper scoring rules are adopted in the analyses in this paper, such as the logarithmic score (LS), the continuously ranked probability score (CRPS) and the censored likelihood score (CLS).

The logarithmic score is defined as in $\eqref{eq:ls}$ where $p_t$ is the predictive density. 
\begin{equation} \label{eq:ls}
S_{LS}(p_{t-1}, y_t) = log[p_{t-1}(y_t)]
\end{equation}
It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters [@bickel2007]. One common usage of the logarithmic score in frequentist econometrics is the maximum likelihood estimation (MLE).
\begin{equation} \label{eq:mle}
\hat \theta_{MLE}=arg \max_\theta \{log[p_{t-1}(y_t|\theta)]\}
\end{equation}
It provides an asymptotically optimal and efficient estimation under the correctly specified log-likelihood function and regularity.

However, the logarithmic score is criticized for its unboundedness and its local property. @bernardo1979 states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state". @gneiting2007 also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event. @gneiting2007 propose the continuously ranked probability score, which is sensitive to distance and is defined as in $\eqref{eq:crps}$ 
\begin{equation} \label{eq:crps}
CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P_{t-1}(y)-I(y\geq x_t)]^2dy
\end{equation}
where $\mathcal{P}$ is the cumulative distribution function, *I* is the indicator function, and $x_t$ is the materialized event.

The formula can be simplified to $\eqref{eq:crnorm}$ if the prediction distribution is Gaussian with mean $\mu$ and variance $\sigma^2$.
\begin{equation} \label{eq:crnorm}
CRPS(N_{t-1},x_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x_t-\mu}{\sigma})-\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
\end{equation}
where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the standard Gaussian distribution.

Both LS and CRPS are used for producing predictive densities and evaluating the out-of-sample predictive performance. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood [@gneiting2011]. @diks2011 propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast. Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy. It is defined as in $\eqref{eq:cls}$
\begin{equation} \label{eq:cls}
S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
\end{equation}
where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$. @opschoor2017 prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.

@@

Optimal forecasts can outperform predictions produced by conventional methods out of sample; see @opschoor2017, @fbp2019 abd @optimal; but the underlying reasons driving this phenomenon are still under investigation. Recent research show that the degree of model misspecification impacts the performance of optimal forecasts. The greater the degree of misspecification is, the more benefits are gained from optimal forecasts in both Bayesian and frequentist predictions, conditional on the assumed predictive model being compatible; see [@fbp2019] and [@optimal]. The simulation analysis in this paper will extend the exploration in this field and ask the question ‘Will the performance of optimal forecasts change when a different form of misspecification occurs?’.

In order to set the scene for the financial application analyses in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and their volatility. Specific simulation scenarios are listed in Table 1 ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).

\begin{table}[!ht]
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{\textbf{Table 1: Simulation design}} \\ \hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} & \textbf{Scenario (iii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$ & Stochastic volatility inversion copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = \{0, -3, -5\} \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & & $\nu \in \{3,12\}$ & \\ \hline

\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
\end{tabular}}
\caption{It shows three simulation scenarios conducted in the numerical analysis sections where Scenario (i) shows the correct model specification, Scenario (ii) shows that the true DGP is GARCH with Student-t distribution while the assumed model creates normal distribution, and Scenario (iii) creates an asymmetric true DGP, while the assumed model can only produces symmetric predictive distribution.}
\end{table}

@@

Copula models are a flexible approach to represent the joint distribution function of a set of variables [@fan2014]. In recent years, these models have been applied for modelling of serial dependence as shown in $\eqref{eq:copula}$ [@inversion2018]. 
\begin{equation} \label{eq:copula}
p_{t-1}(y_t)=c(P(y_t),P(y_{t-1}))p(y_{t-1})
\end{equation}
where $\mathcal{P}()$ and $\mathcal{p}$ denote the marginal distribution and density function of $y_t$ respectively, and c() is the copula density function that captures the dependence between $y_t$ and $y_{t-1}$.

For the simulation exercise, the marginal distribution $\mathcal{P}()$ is chosen to be the standard skew-normal distribution, while c() is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018. The stochastic volatility inversion copula model used in this section allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns [@inversion2018].

In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP specifications in Scenario (ii) and (iii).

We apply the scoring rules introduced in Section 2.2 and set CLS to focus on 10%, 20%, 80% and 90% tails of the empirical marginal distribution, corresponding to the risks of long and short portfolios of financial investments, and we label them as CLS10, CLS20, CLS80 and CLS90 in following tables and figures. Due to the fact that there is no reliable estimate of the true conditional densities, only the tails of the marginal distributions are set to be the standard when assessing the predictive accuracy by CLS, rather than the conditional distributions. Meanwhile, MLE is included as a benchmark for comparing whether optimal forecasts can provide benefits or not, since MLE is asymptotically optimal and efficient under the correct model specification and regularity. Even though this property does not hold under misspecification, MLE can still give insights about how conventional likelihood-based methods perform.

We conduct Monte Carlo simulations using the methodology in @optimal and @fbp2019. Specific steps are as follows:

Let $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ be the one-step-ahead predictive distribution function based on the assumed model and optimized according to the scoring rule $S_i$, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$ be the corresponding predictive density function at time $\mathcal{t}$.

@@

  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}^{[i]}$ in the assumed predictive model based on the positively oriented score $S_i$ where $\boldsymbol{\hat \theta}^{[i]} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}^{[i]}$

\begin{equation} \label{eq:theta}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{equation}
\begin{equation} \label{eq:score}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S_i(P_{\boldsymbol\theta}^{t-1},y_t)
\end{equation}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:CLS}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]

\begin{equation} \label{eq:LS}
S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
\end{equation}
\begin{equation} \label{eq:CRPS}
S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
\end{equation}
\begin{equation} \label{eq:CLS}
S_{CLS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
\end{equation}
4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores:^[Out-of-sample size $\tau = 5000$ is sufficiently large to let the optimal forecasts take place; see @optimal for full discussion about sample size effects on optimal forecasts.]
\begin{equation} \label{eq:avgscore}
\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
\end{equation}
